### 2015-07-05 narrative/proposed-work.tex
edits

\underline{Principle 1:} A knowledge-centric system that allows user expertise to define data policies. Today Storage System and I/O
layers are written in a stove-pipe fashion and usually do not allow for optimizations. We propose to re-design this
layer in a highly integrated fashion that allows for user input. This re-designed layer will then statically, and dynamically optimize the use of resources for both the system and for individual users.

\underline{Principle 2}: Predictable Performance in the SSIO layer needs to be established so more science can be done on the
exascale Systems. Unpredicitable performance in the I/O layer is often met with unpredictable guesses from users which decreases the effectiveness of simulation runs and the associated science.

\underline{Principle 3:} In a data-centric SSIO system, we need user goals to define the data policies. We introduce data-driven
SSIO optimizations by enabling users to define data manipulations (re-organizations) at a high level and then we express
policy goals by associating intentions (hints) with data;' e.g. ``this data at this level should be accessible in the next three months.''
These high level specifications of desired results will be used in our system for data migration and eviction policies.

>>>>

\underline{Principle 1:} A knowledge-centric system that allows user expertise to define data policies. Today SSIO
layers are written in a stove-pipe fashion and usually do not allow for optimizations. We propose to re-design this
layer in a highly integrated fashion that allows for user input. This re-designed layer will then statically, and dynamically optimize the use of resources for both the system and for individual users.

\underline{Principle 2}: Predictable Performance in the SSIO layer needs to be established to increases the efficiency of science on exascale systems. Unpredicitable performance in the I/O layer is often met with unpredictable guesses from users which decreases the effectiveness of simulation runs and the associated science.

\underline{Principle 3:} In a data-centric SSIO system, we need user goals to define the data policies. We introduce data-driven
SSIO optimizations by enabling users to define data manipulations (re-organizations) at a high level and then express
policy goals by associating intentions (hints) with data;' e.g. ``this data at this level should be accessible in the next three months.''
These high level specifications of desired results will be used in our system for data migration and eviction policies.
